%
% brownletter_example.tex - an example latex file to illustrate brownletter.cls
%
% Copyright 2003, Nesime Tatbul (tatbul@cs.brown.edu)
%

\documentclass[11pt]{brownletter}

\name{Nesime Tatbul} % used as signature, if no signature is specified

\signature{Nesime Tatbul\\ Tex Merc}

\date{December 15, 2003} % if no date specified, today's date is used 

\subject{Brown letterhead} % optional subject line

\begin{document}

\begin{letter}{Prof. Eli Upfal\\ 
               Brown University\\ 
               Box 1910\\ 
               Providence, RI 02912}

\opening{Dear Sir,}

This is the story of how I did grad school without being in grad school. 

This could be a long or short letter, so the gist is I transferred schools in the same city and was obsessed with the field of optics the entire time and having an identity crisis of how experienced in the field I am based on my degree. 

I was introduced to the field like any average suburban kid: in my AP physics course and technical clubs. They passed around the diffraction gradient and I did an overnight stay at University of Rochester and sat in on the Sources and Detectors course. I applied to the school and decided on Optics in my second year there. I had the typical liberal arts experience, I learned how to write and edit my work and attached myself to the student chapters of OSA and SPIE. I lived with the optics majors and looking back on it 80 percent of them were my close friends out of survival and convenience. I did charter a sorority there Kappa Alpha Theta, the Theta Lambda chapter, but left it after transferring schools and truthfully I did not have the money for their dues along with my tuition. 

I'll admit that the person I was prior to now was an immature and blissfully ignorant child with a great deal of privilege. Most of the time I knew that I knew nothing and desperately wanted to learn and be called out for anything I was doing wrong since growing up I received enough transparent treatment of who my dad was or how pretty I was than for my actual skills and thoughts. Think complimenting me on how fast I made copies or delivered mail level. 

I'm skilled at starting new ideas and this whole github project is holding me accountable. 


This could be a long or short letter, but at the end of the day I repeat this statement of purpose to myself everyday...to run to class, to go to that stuffy networking event, and to be empathetic to a colleague that is getting on my nerves.   


Now I'm nearing my 26th birthday and I'm realizing how abnormal my path is to everyone else. 




Footnote: 
This is my statement of purpose and could be a cover letter as well. I am currently writing this during the covid pandemic as well as the wwiii in Ukraine and Russia at an urgency. Inflation is crazy so I'm just trying to live. A life of reaction is not the best, but it only took this for me to actually write the thing that scares me the most. 

 




\closing{Sincerely,}

\encl{brownletter.cls}

\ps{Please see the enclosed file.}

\cc{J. Kirschenbaum}

\end{letter}

\end{document}